### 2017-09-19 icde/sec-exp.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
